---
title: "debug_PowerGridNetworking"
author: "Jonathan Bourne"
date: "22/02/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

Power grid networking was made before I really understood how to make package. As a result it is very sensitive. I am going to use the package "usethis" to make it much easier to run and also create a website from the documentation




I removed
Multi-attack
ggpowerlaw

```{r}
library(usethis)
library(devtools)
```



```{r}
path <- file.path("/home/jonno/PowerGridNetworking")
#create_package(path)
#usethis::use_pkgdown()
setwd(path)
```

#Other packages

Add in functionality from other packages
```{r}
use_pipe()
use_package("dplyr")
use_package("igraph")
use_package("purrr")
use_package("stats")
use_package("rlang")
use_package("utils")
use_package("animation")
use_package("stringr")
use_package("readr")
use_tidy_eval()

use_gpl3_license(name = "Jonathan Bourne")

```

#replace functions

This goes through all the functions in the package and replaces the external package names with "`package name`::" this is necessary for the package to work. All the packages must be included in the description file.

```{r}

ls(package:rlang)
#list all functions in the package
#create a tibble appending "package name::"
#"remove all the functions that use % as these won't work and pipe is included separately anyway
append_package_name <-c("dplyr",
        "igraph",
        "purrr",
        "stats",
        "rlang",
        "tibble",
        "tidyr"
        #"utils"
         ) %>%
  map_df(~{
    
    ls(paste0("package:", .x)) %>%
      tibble(map_from = ., map_to = paste0(.x,"::", map_from))
    
  }) %>%
  filter(!grepl("%", map_from),
         !grepl("!", map_from),
         !grepl("=", map_from),
         !grepl("<", map_from),
         map_to != "tibble::as_data_frame",
         map_to != "dplyr::as_data_frame"
         )


target_files <- list.files(file.path(getwd(),"R"), full.names = T) 
target_files <- target_files[!grepl("utils-pipe.R", target_files)]


target_files %>%
  walk(~{
    print(basename(.x))
    tx  <- read_lines(.x, ) 
    
    #don't make any changes before the first row of the function code
    first_row <- min(grep("function\\(", tx))
    
    #take only the part that will be changed
    tx2 <- tx[(first_row+1):length(tx)]
    
    
    for(n in 1:nrow(append_package_name)){
      
      target_out <- append_package_name %>%
        slice(n) 
      
      #uses negative lookahead
      #cannot be preceded by letters or underscore or period or double colon
      #must be followed by open bracket
      look_for <- paste0('(?<![a-zA-Z]|(::)|_|\\.)','(',target_out$map_from,')','(\\()')
      
      #replace the necessary parts
      tx2 <- str_replace_all(tx2, pattern = look_for, paste0(target_out$map_to, "("))
      
      
    }
    
    #combine function preamble with the edited function code
    
    tx2 <- c(tx[1:first_row], tx2)
    
    writeLines(tx2, con=.x)
    
  })


test <- "(vcount())"

pattern_to_replace <- paste0('(?<![a-zA-Z]|(::)|_|\\.)','(',"vcount",')','(\\()')

str_replace_all(test, 
                pattern = pattern_to_replace, 
                replacement = "xxxx(")

```


check files for what ever is needed

```{r}



target_files %>%
  map_df(~{
    tx  <- read_lines(.x ) 
    
    tibble(function_name = basename(.x),
           rlang = sum(grepl(":=", tx) ),
           igraph = sum(grepl("g Slackref", tx) )
           )
    
  }) %>%
  filter(!(rlang ==0 &igraph == 0))


target_files2 <- list.files("/home/jonno/rSETSe/R", full.names = T) 
target_files2 %>%
  map_df(~{
    tx  <- read_lines(.x ) 
    
    tibble(function_name = basename(.x),
           rlang = sum(grepl(":=", tx) ),
           rlang2 = sum(grepl("!!!", tx) ))
    
  }) %>%
  filter(rlang2>0 | rlang>0)
```

```{r}
#add citation only needs to be done once
#use_citation()
```


#check for errors in the package


```{r}

document()
check()


```

```{r}
#usethis::use_github_action("pkgdown")#only needs to be run once
pkgdown::build_site()

```

